Implications of uniformly distributed, empirically informed priors for phylogeographical model selection: A reply to Hickerson et al.

### 2014-08-02 manuscripts/reply/reply-main.tex
More editing of reply ms.

Recently, \citet{Oaks2012} used this model-choice framework to study 22 pairs
of vertebrate lineages distributed across the Philippines; they also studied
the behavior of the \msb approach using computer simulations.
They found the method is very sensitive to prior assumptions and often
supports shared divergences across taxa that diverged randomly over broad time
periods, to which \citet{Hickerson2013} responded.
\citet{Oaks2012} and \citet{Hickerson2013} agree on the fundamental
methodological point about the model selection performed in \msb:
\begin{itemize}
   \item The use of vague priors on the divergence-time parameters can lead to
       spurious support for models with few divergence events shared across
       taxa. Thus, the primary inference enabled by the approach is very
       sensitive to the priors on divergence times.
\end{itemize}
However, the two papers suggest alternative mechanisms by which the priors on
divergence times cause this behavior:
\begin{description}
    \item[Hypothesis 1: Numerical approximation error \citep{Hickerson2013}]
        Under broad uniform priors, the rejection algorithm implemented in \msb
        is unable to adequately sample the space of the models within
        reasonable computational time, which leads to bias toward models with
        fewer divergence-time parameters because they are better sampled.
    % \item \citet{Hickerson2013} suggest that under broad uniform priors, the
    %     rejection algorithm implemented in \msb is unable to adequately sample
    %     the space of the models within reasonable computational time, which
    %     leads to bias toward models with fewer divergence-time parameters
    %     because they are better sampled.
    \item[Hypothesis 2: Strongly weighted marginal likelihoods
        \citep{Oaks2012}]
        The uniform priors on divergence times simply lead to very small
        marginal likelihoods of models with many divergence-time parameters.
        These models are ``averaged'' over much greater parameter space with
        large prior weight and small likelihood
        \citep{Jeffreys1939,Lindley1957}.
    % \item \citet{Oaks2012} suggest the cause is more fundamental; the uniform
    %     priors on divergence times simply lead to very small marginal
    %     likelihoods of models with many divergence-time parameters. These
    %     models are ``averaged'' over much greater parameter space with large
    %     prior weight and small likelihood \citep{Jeffreys1939,Lindley1957}.
\end{description}
In Hypothesis 1, the problem is numerical approximation error due to
insufficient computation;
% In the former case, the problem is numerical approximation error due to
% insufficient computation;
the exact posterior supports models with many divergence-time parameters
given data generated under temporally random divergences, but we are unable to
accurately approximate the posterior.
In Hypothesis 2, the problem is more fundamental, because the exact posterior
supports simultaneous divergences given data from randomly diverged taxa.
% In the latter case, numerical error is not the issue, because the exact
% posterior supports simultaneous divergences given data from randomly diverged
% taxa.
I.e., given the assumption that divergence times are broadly and uniformly
distributed, the exact posterior from Bayes' rule leads us to the wrong
conclusions about evolutonary history.
% I.e., this is the correct (albeit biogeographically misleading) answer given
% the prior assumption that divergence times are broadly and uniformly
% distributed.
Such posterior support for simultaneous divergence, even if ``correct'' from
the perspective of Bayesian model choice, does not provide the biogeographical
insights that a researcher who employs \msb seeks to gain.

While these phenomena are not mutually exclusive, it is important to
distinguish between them in order to determine how to improve our ability to
estimate shared divergence histories.
If Hypothesis 1 is correct, then the model is sound and we need to increase our
computational effort or improve our Monte Carlo integration procedures.
For example, Markov chain or sequential Monte Carlo algorithms might sample the
posterior more efficiently than the simple Monte Carlo rejection sampler
implemented in \msb.
Rather than alter the sampling algorithm, \citet{Hickerson2013} tried using
narrow, empirically informed uniform priors in the hope that with less
parameter space to sample, the rejection algorithm will produce better
estimates of the posterior.
Here, we discuss theoretical considerations for using empirically informed
priors for Bayesian model choice and evaluate the approach of
\citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
\citet{Oaks2012}.
In their analyses, \citet{Hickerson2013} made an error by mixing different
units of time, which invalidates the results presented in their response (see
Supporting Information for details).
We correct this error, but still find their approach will often support
(1) clustered divergence models when divergences are random, and
(2) models that exclude from consideration the true values of the
parameters.
The behavior of their approach also suggests that insufficient computation
(Hypothesis 1) is not the primary cause of the issue.

If Hypothesis 2 is correct, we need to correct the model, because no amount of
computation will help; even if we could calculate the exact posterior, we would
still reach the wrong interpretation about evolutionary history.
Accordingly, \citet{Oaks2014dpp} has introduced a method that uses more
flexible probability distributions to accommodate prior uncertainty in
divergence times without overly inhibiting the marginal likelihoods of models
with more divergence-time parameters.
This greatly increases the method's robustness and power to detect temporal
variation in divergences \citep{Oaks2014dpp}.
This is not surprising given the rich statistical literature showing that
marginal likelihoods are very sensitive to the priors used in Bayesian model
selection
\citep[e.g.,][]{Jeffreys1939,Lindley1957}.

We also explore the distinct predictions made by Hypotheses 1 and 2.
We show the behavior of \msb matches the predictions of Hypothesis 2,
but not Hypothesis 1.
This strongly suggests the method tends to support models of shared divergences
not due to insufficient computation, but rather due to the larger marginal
likelihoods of these models under the prior assumption of uniformly distributed
divergence times.
% We also show that numerical approximation error is not a major contributer to
% the problem.

\section{The potential implications of empirical Bayesian model choice}
\citet{Oaks2012} found \msb spuriously supports models of temporally
clustered divergences even when using a prior on divergence times that was
informed by the data being analyzed.
The main argument of \citet{Hickerson2013} is that the priors used by
\citet{Oaks2012} were not informative enough.
They suggest a very narrow, highly informed uniform prior on divergence times
is necessary to avoid the method's preference for models with few
divergence-time parameters.
Such an empirical Bayesian approach to model selection raises some theoretical
and practical concerns, some of which were discussed by \citet{Oaks2012} (see
the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}); we expand on this here.

@@

Nonetheless, empirical Bayesian model choice does perform well for some
problems.
Particularly, in cases where large aggregate data sets are used for many
parallel model-choice problems simultaneously, pooling information to inform
priors can lead to favorable group-wise frequentist coverage across tests
\citep{Efron2008}.
However, this is far removed from the single model-choice problem of \msb.
In the Supporting Information we use a simple example to help highlight the
distinctions between Bayesian parameter estimation and model choice.

@@

The strong preference for the narrowest prior on divergence times suggests the
approach of \citet{Hickerson2013} is biased toward models with less parameter
space and, as a consequence, will estimate model-averaged posteriors dominated
by models that exclude true values of the parameters.
We explored this possibility in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging
approach of \citet{Hickerson2013}, but set one of the prior models with a
uniform prior on divergence times that is unrealistically narrow and almost
certainly excludes most, if not all, of the true divergence times of the 22
taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space, we expect \msb will preferentially sample from this
erroneous model yielding a posterior that is misleading (i.e., the
model-averaged posterior will be dominated by a model that excludes
the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

@@

Our results show that the model-averaging approach of \citet{Hickerson2013}
strongly prefers the prior model with the narrowest distribution on divergence
times across all three of our analyses, even when this model excludes the true
divergence times of the Philippine taxa
(Table~\ref{tabModelChoiceEmpirical}).
However, \citet{Hickerson2013} vetted the priors used in their model-averaging
approach via ``graphical checks,'' in which the summary statistics from 1000
random samples of each prior model are plotted along the first two orthogonal
axes of a principle component analysis (see Figure 1 of \citet{Hickerson2013}).
To determine if such prior-predictive analyses would indicate the $M_{1A}$ and
$M_{1B}$ models are problematic, we performed these graphical checks on our
prior models.
Unfortunately, these prior-predictive checks provide no warning that these
priors are too narrow (Figure~S\ref{figPCA}).
Rather, the graphs suggest these invalid priors are ``better fit''
(Figure~S\ref{figPCA}A--C) than the valid priors similar to those used by
\citet{Oaks2012} (Figure~S\ref{figPCA}D--F).

@@

To better quantify the propensity of Hickerson et al.'s
(\citeyear{Hickerson2013}) approach to exclude the truth, we simulated 1000
datasets in which the divergence times for the 22-population pairs are drawn
randomly from an exponential distribution with a mean of 0.5 ($\divt{} \sim
Exp(2)$).
All other parameters were identically distributed as the $M_1$--$M_5$ models
(Table~\ref{tabModelChoiceEmpirical}).
We then repeated the model-averaging  analysis described above, retaining 1000
posterior samples for each of the 1000 simulated datasets.
For each simulation replicate, we estimated the Bayes factor in favor
of excluding the truth as the ratio of the posterior to prior odds of
excluding the true value of at least one parameter.
Whenever the Bayes factor preferred a model excluding the truth we counted the
number of the 22 true divergence times that were excluded by the preferred
model.

@@

The results of the above empirical and simulation analyses clearly demonstrate
the risk of using narrow, empirically guided uniform priors in a Bayesian
model-averaging framework.
The consequence of this approach is obtaining a model-averaged posterior
estimate that is heavily weighted toward models that exclude true
values of the parameters.
This is not a general critique of Bayesian model averaging.
Rather, model averaging can provide an elegant way of incorporating
model uncertainty in Bayesian inference.
However, when averaging over models with narrow and broad uniform priors on a
parameter with a likelihood density that is not expected to be uniformly
distributed, the posterior can be dominated by models that exclude from
consideration the true values of parameters due to the larger marginal
likelihoods of the models that integrate over less space with high prior
weight yet low likelihood.

@@

\section{Assessing the power of the model-averaging approach of
    \citet{Hickerson2013}}
While our results above clearly demonstrate the risks inherent to the empirical
Bayesian model-choice approach used by \citet{Hickerson2013}, one could justify
such risk if the approach does indeed increase power to detect temporal
variation in divergences.
We assess this possibility using simulations.
Following \citet{Oaks2012}, we simulated 1000 datasets with \divt{} for each of
the 22 population pairs randomly drawn from a uniform distribution, $U(0,
\divt{max})$, where \divt{max} was set to: 0.2, 0.4, 0.6, 0.8, 1.0, and 2.0, in
\globalcoalunit generations.
All other parameters were identically distributed as the prior models.
As above, we generated $5\e6$ samples from the prior models in
Table~\ref{tabModelChoiceEmpirical}.
For each of the 6000 simulated datasets, we approximated the posterior
by retaining 1000 samples from the prior.

Our results demonstrate that the approach of \citet{Hickerson2013} consistently
infers highly clustered divergences across all the \divt{max} we simulated
(Figure~\ref{figPower4}A--D \& S\ref{figPower6}A--F).
If we follow \citet{Hickerson2013} and use a Bayes factor of greater than 10 as
the criterion for incorrect inference of a single divergence event, we find
that the approach will often strongly support the extreme case of one
divergence event across all our simulation conditions (Figure~\ref{figPower4}E--H \&
S\ref{figPower6}G--L).
The method also struggles to estimate the variance of divergence times
(\vmratio{}), whether evaluating the unadjusted
(Figure~S\ref{figPowerAccuracy}A--F) or GLM-adjusted
(Figure~S\ref{figPowerAccuracy}G--L) posterior estimates.
Overall, the empirical Bayesian model-averaging approach leads to erroneous
support for highly clustered divergences when populations diverged randomly
over the last $8\globalpopsize$ generations.
For loci with per-site rates of mutation on the order of $1\e{-8}$ and
$1\e{-9}$ per generation, this translates to 10 million and 100 million
generations, respectively.

@@

\section{The causes of support for models of co-divergence}
To determine how best to improve the behavior of \msb, it is important to
determine the mechanism by which broad uniform priors cause support for
clustered models of divergence.
It is well established that vague priors can be problematic in Bayesian model
selection.
Models that integrate over more parameter space characterized by low
probability of producing the data and relatively high prior density will have
smaller marginal likelihoods \citep{Jeffreys1939,Lindley1957}.
Given the uniformly distributed priors on divergence times employed in \msb,
the likelihood of models with more divergence parameters will be ``averaged''
over much greater parameter space, all with equal prior weight, and much of it
with small likelihood.
In light of this fundamental statistical issue, it is not surprising that the
method tends to support simple models.

>>>>

Recently, \citet{Oaks2012} used this model-choice framework to study 22 pairs
of vertebrate lineages distributed across the Philippines; they also studied
the behavior of the \msb approach using computer simulations.
They found the method is very sensitive to prior assumptions and often
supports shared divergences across taxa that diverged randomly over broad time
periods, to which \citet{Hickerson2013} responded.
\citet{Oaks2012} and \citet{Hickerson2013} agree on the fundamental
methodological point about the model selection performed in \msb:
\begin{itemize}
   \item The use of vague priors on the divergence-time parameters can lead to
       spurious support for models with few divergence events shared across
       taxa. Thus, the primary inference enabled by the approach is very
       sensitive to the priors on divergence times.
\end{itemize}
However, the two papers suggest alternative mechanisms by which the priors on
divergence times cause this behavior:
\begin{enumerate}[label=\textsl{\textbf{Hypothesis \arabic*)}},ref=\arabic*,align=left]
    \item \textsl{\textbf{Numerical approximation error}} \citep{Hickerson2013}:
        Under broad uniform priors, the rejection algorithm implemented in \msb
        is unable to adequately sample the space of the models within
        reasonable computational time, which leads to bias toward models with
        fewer divergence-time parameters because they are better sampled.
        \label{hypError}
    % \item \citet{Hickerson2013} suggest that under broad uniform priors, the
    %     rejection algorithm implemented in \msb is unable to adequately sample
    %     the space of the models within reasonable computational time, which
    %     leads to bias toward models with fewer divergence-time parameters
    %     because they are better sampled.
    \item \textsl{\textbf{Strongly weighted marginal likelihoods}}
        \citep{Oaks2012}:
        The uniform priors on divergence times lead to very small marginal
        likelihoods (and thus posterior probabilities) of models with many
        divergence-time parameters.  The likelihood of these models is
        ``averaged'' over a much greater parameter space in which there is a
        large amount of prior weight and small probability of producing the
        data.  \citep{Jeffreys1939,Lindley1957}. \label{hypML}
    % \item \citet{Oaks2012} suggest the cause is more fundamental; the uniform
    %     priors on divergence times simply lead to very small marginal
    %     likelihoods of models with many divergence-time parameters. These
    %     models are ``averaged'' over much greater parameter space with large
    %     prior weight and small likelihood \citep{Jeffreys1939,Lindley1957}.
\end{enumerate}
In Hypothesis~\ref{hypError}, the problem is numerical approximation error due to
insufficient computation;
given data from randomly diverged taxa, the exact posterior supports a model
with many divergence-time parameters, but we are unable to accurately
approximate this posterior.
In Hypothesis~\ref{hypML}, the problem is more fundamental; given data from
randomly diverged taxa, the exact posterior supports a model with a small
number of simultaneous divergences.
% In the latter case, numerical error is not the issue, because the exact
% posterior supports simultaneous divergences given data from randomly diverged
% taxa.
I.e., given the assumption that divergence times are broadly and uniformly
distributed, the exact posterior from Bayes' rule leads us to the wrong
conclusion about evolutionary history.
% I.e., this is the correct (albeit biogeographically misleading) answer given
% the prior assumption that divergence times are broadly and uniformly
% distributed.
Such posterior support for simultaneous divergence, even if ``correct'' from
the perspective of Bayesian model choice, does not provide the biogeographical
insights that a researcher who employs \msb seeks to gain.

While these phenomena are not mutually exclusive, it is important to
distinguish between them in order to determine how to improve our ability to
estimate shared divergence histories.
If Hypothesis~\ref{hypError} is correct, then the model is sound and we need to
increase our computational effort or improve our Monte Carlo integration
procedures.
For example, Markov chain or sequential Monte Carlo algorithms might sample the
posterior more efficiently than the simple Monte Carlo rejection sampler
implemented in \msb.
Rather than alter the sampling algorithm, \citet{Hickerson2013} tried using
narrow, empirically informed uniform priors in the hope that with less
parameter space to sample, the rejection algorithm would produce better
estimates of the posterior.
Here, we discuss theoretical considerations for using empirically informed
priors for Bayesian model choice and evaluate the approach of
\citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
\citet{Oaks2012}.
In their analyses, \citet{Hickerson2013} made an error by mixing different
units of time, which invalidates the results presented in their response (see
Supporting Information for details).
We correct this error, but still find their approach will often support
(1) clustered divergence models when divergences are random, and
(2) models that exclude from consideration the true values of the
parameters.

If Hypothesis~\ref{hypML} is correct, we need to correct the model, because no
amount of computation will help; even if we could calculate the exact
posterior, we would still reach the wrong interpretation about evolutionary
history.
Accordingly, \citet{Oaks2014dpp} has introduced a method that uses more
flexible probability distributions to accommodate prior uncertainty in
divergence times without overly inhibiting the marginal likelihoods of models
with more divergence-time parameters.
This greatly increases the method's robustness and power to detect temporal
variation in divergences \citep{Oaks2014dpp}.
This is not surprising given the rich statistical literature showing that
marginal likelihoods are very sensitive to the priors used in Bayesian model
selection
\citep[e.g.,][]{Jeffreys1939,Lindley1957}.

We also explore the distinct predictions made by Hypotheses 1 and 2.
We show the behavior of \msb matches the predictions of Hypothesis~\ref{hypML},
but not Hypothesis~\ref{hypError}.
This strongly suggests the method tends to support models of shared divergences
not because of insufficient computation, but rather due to the larger marginal
likelihoods of these models under the prior assumption of uniformly distributed
divergence times.

\section{The potential implications of empirical Bayesian model choice}
% \citet{Oaks2012} found \msb spuriously supports models of temporally
% clustered divergences even when using a prior on divergence times that was
% informed by the data being analyzed.
% The main argument of \citet{Hickerson2013} is that the priors used by
% \citet{Oaks2012} were not informative enough.
\citet{Hickerson2013} suggest a very narrow, highly informed uniform prior on
divergence times is necessary to avoid the method's preference for models with
few divergence-time parameters.
Such an empirical Bayesian approach to model selection raises some theoretical
and practical concerns, some of which were discussed by \citet{Oaks2012} (see
the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}); we expand on this here.

@@

Nonetheless, empirical Bayesian model choice does perform well for some
problems.
Particularly, in cases where large aggregate data sets are used for many
parallel model-choice problems, pooling information to inform
priors can lead to favorable group-wise frequentist coverage across tests
\citep{Efron2008}.
However, this is far removed from the single model-choice problem of \msb.
In the Supporting Information we use a simple example to help highlight the
distinctions between Bayesian parameter estimation and model choice.

@@

The strong preference for the narrowest prior on divergence times suggests the
approach of \citet{Hickerson2013} is biased toward models with less parameter
space and, as a consequence, will estimate model-averaged posteriors dominated
by models that exclude true values of the parameters.
We explored this possibility in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging
approach of \citet{Hickerson2013}, but set one of the prior models with a
uniform prior on divergence times that is unrealistically narrow and almost
certainly excludes most, if not all, of the true divergence times of the 22
taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space (Hypothesis~\ref{hypML}), we expect \msb will
preferentially sample from this erroneous model yielding a posterior that is
misleading (i.e., the model-averaged posterior will be dominated by a model
that excludes the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

@@

Our results show that the model-averaging approach of \citet{Hickerson2013}
strongly prefers the prior model with the narrowest distribution on divergence
times across all three of our analyses, even when this model excludes the true
divergence times of the Philippine taxa
(Table~\ref{tabModelChoiceEmpirical}).
Given that the same number of simuations were sampled from each prior model,
this behavior is not clearly predicted by insufficient computation
(Hypothesis~\ref{hypError}), but is a straightforward prediction of
Hypothesis~\ref{hypML}.

\citet{Hickerson2013} vetted the priors used in their model-averaging
approach via ``graphical checks,'' in which the summary statistics from 1000
random samples of each prior model are plotted along the first two orthogonal
axes of a principle component analysis (see Figure 1 of \citet{Hickerson2013}).
To determine if such prior-predictive analyses would indicate the $M_{1A}$ and
$M_{1B}$ models are problematic, we performed these graphical checks on our
prior models.
Unfortunately, these prior-predictive checks provide no warning that these
priors are too narrow (Figure~S\ref{figPCA}).
Rather, the graphs suggest these invalid priors are ``better fit''
(Figure~S\ref{figPCA}A--C) than the valid priors used by \citet{Oaks2012}
(Figure~S\ref{figPCA}D--F).

@@

To better quantify the propensity of Hickerson et al.'s
(\citeyear{Hickerson2013}) approach to exclude the truth, we simulated 1000
datasets in which the divergence times for the 22-population pairs are drawn
randomly from an exponential distribution with a mean of 0.5 ($\divt{} \sim
Exp(2)$).
All other parameters were identically distributed as the $M_1$--$M_5$ models
(Table~\ref{tabModelChoiceEmpirical}).
We then repeated the model-averaging  analysis described above, retaining 1000
posterior samples for each of the 1000 simulated datasets.
For each simulation replicate, we estimated the Bayes factor in favor
of excluding the truth as the ratio of the posterior to prior odds of
excluding the true value of at least one parameter.
Whenever the Bayes factor preferred a model excluding the truth, we counted the
number of the 22 true divergence times that were excluded by the preferred
model.

@@

The results of the above empirical and simulation analyses clearly demonstrate
the risk of using narrow, empirically guided uniform priors in a Bayesian
model-averaging framework.
The consequence of this approach is obtaining a model-averaged posterior
estimate that is heavily weighted toward models that exclude true
values of the parameters.
This is not a general critique of Bayesian model averaging.
Rather, model averaging can provide an elegant way of incorporating
model uncertainty in Bayesian inference.
However, as predicted by Hypothesis~\ref{hypML}, when averaging over models
with narrow and broad uniform priors on a parameter that is not expected to
have a uniformly distributed likelihood density, the posterior can be dominated
by models that exclude from consideration the true values of parameters due to
their larger marginal likelihoods (these models integrate over less space with
high prior weight and low likelihood).

@@

\section{Assessing the power of the model-averaging approach of
    \citet{Hickerson2013}}
While our results above clearly demonstrate the risks inherent to the empirical
Bayesian model-choice approach used by \citet{Hickerson2013}, one could justify
such risk if the approach does indeed increase power to detect temporal
variation in divergences.
We assess this possibility using simulations.
Following \citet{Oaks2012}, we simulated 1000 datasets with \divt{} for each of
the 22 population pairs randomly drawn from a uniform distribution, $U(0,
\divt{max})$, where \divt{max} was set to: 0.2, 0.4, 0.6, 0.8, 1.0, and 2.0, in
\globalcoalunit generations.
All other parameters were identically distributed as the prior models.
As above, we generated $5\e6$ samples from prior models $M_1$--$M_5$
(Table~\ref{tabModelChoiceEmpirical}).
For each of the 6000 simulated datasets, we approximated the posterior
by retaining 1000 samples from the prior.

Our results demonstrate that the approach of \citet{Hickerson2013} consistently
infers highly clustered divergences across all the \divt{max} we simulated
(Figure~\ref{figPower4}A--D \& S\ref{figPower6}A--F).
The approach often strongly supports (Bayes factor of greater than 10) the
extreme case of one divergence event across all our simulation conditions
(Figure~\ref{figPower4}E--H \& S\ref{figPower6}G--L).
The method also struggles to estimate the variance of divergence times
(\vmratio{}), whether evaluating the unadjusted
(Figure~S\ref{figPowerAccuracy}A--F) or GLM-adjusted
(Figure~S\ref{figPowerAccuracy}G--L) posterior estimates.
Overall, the empirical Bayesian model-averaging approach leads to erroneous
support for highly clustered divergences when populations diverged randomly
over the last $8\globalpopsize$ generations.
For loci with per-site rates of mutation on the order of $1\e{-8}$ and
$1\e{-9}$ per generation, this translates to 10 million and 100 million
generations, respectively.

@@

%%
\section{The causes of support for models of co-divergence}
To determine how best to improve the behavior of \msb, it is important to
determine the mechanism by which broad uniform priors cause support for
clustered models of divergence.
It is well established that vague priors can be problematic in Bayesian model
selection.
Models that integrate over more parameter space characterized by low
probability of producing the data and relatively high prior density will have
smaller marginal likelihoods \citep{Jeffreys1939,Lindley1957}.
Given the uniformly distributed priors on divergence times employed in \msb,
the likelihood of models with more divergence parameters will be ``averaged''
over much greater parameter space, all with equal prior weight, and much of it
with small likelihood.
In light of this fundamental statistical issue, it is not surprising that the
method tends to support simple models.
